---
name: Colton
surname: Baumler
position: "Bioinformatics and Data Scientist"
pronouns: He/Him
address: "Data Intensive Biology lab of the University of California, Davis"
#phone: +1 555 555 5555
www: ""
email: "ccbaumler@ucdavis.edu"
twitter: ""
github: ccbaumler
linkedin: colton-baumler
orcid: 0000-0002-5926-7792
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "9e2e2e"
docname: Resumé
output:
  vitae::awesomecv
---

```{r setup, include=FALSE}
# Go to https://yihui.org/tinytex/r/#debugging
# if you experience any latex erros

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

require(xfun)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )

xfun::pkg_attach2(packages, message = FALSE)

source(file = here("data", "data.r"))

```

# Professional Summary

**Bioinformaticist and Data Scientist with 5+ years of experience** applying computational biology, data science, and software engineering to large-scale genomic datasets. Specialize in **Python, R, Unix, and Snakemake**, with expertise in k-mer–based sequence analysis and microbial pangenomics, developing accessible data architectures and high-throughput workflows. Developed **novel k-mer–based methods for precise taxonomic profiling and pangenomic interpretation**, engineered scalable genomic databases and saturation analyses, and created open-source software and reproducible computational workflows for analyzing millions of biological sequences.

# Skills

```{r SKILLS, results='asis'}
# Tell the chunk to print raw LaTeX instead of standard R output
cat("\\begin{cvskills}\n")

# Use glue_data to map your dataframe columns to the \cvskill{}{} LaTeX macro
skills %>%
  glue::glue_data("  \\cvskill{<<area>>}{<<skills>>}", .open = "<<", .close = ">>") %>%
  cat(sep = "\n")

cat("\\end{cvskills}\n")
```

# Research Experience

```{r EXPERIENCE}

exp %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# Education

```{r EDUCATION}

edu %>%
  detailed_entries(
    with = glue::glue("{inst} | {detail}",.na = ""),
    what = degree,
    when = dplyr::if_else(
      is.na(endMonth), 
      glue::glue("{startYear} - {endYear}"), 
      glue::glue("{startYear} - {endMonth} {endYear}")
    ),
    where = where
  )

```